---
title: "Sixth_plot"
author: "Marcelladane"
date: "27 July 2017"
output: html_document
---

**Instructions**

*Fine particulate matter (PM2.5) is an ambient air pollutant for which there is strong evidence that it is harmful to human health. In the United States, the Environmental Protection Agency (EPA) is tasked with setting national ambient air quality standards for fine PM and for tracking the emissions of this pollutant into the atmosphere. Approximatly every 3 years, the EPA releases its database on emissions of PM2.5. This database is known as the National Emissions Inventory (NEI). You can read more information about the NEI at the EPA National Emissions Inventory web site.*

For each year and for each type of PM source, the NEI records how many tons of PM2.5 were emitted from that source over the course of the entire year. The data that you will use for this assignment are for 1999, 2002, 2005, and 2008.

**PM2.5 Emissions Data structure**

The files contain the follow columns
*fips*: A five-digit number (represented as a string) indicating the U.S. county
*SCC*: The name of the source as indicated by a digit string (see source code classification table)
*Pollutant*: A string indicating the pollutant
*Emissions*: Amount of PM2.5 emitted, in tons
*type*: The type of source (point, non-point, on-road, or non-road)
*year*: The year of emissions recorded

**Question**

6 - Compare emissions from motor vehicle sources in Baltimore City with emissions from motor vehicle sources in Los Angeles County, California (fips == "06037"). Which city has seen greater changes over time in motor vehicle emissions?

First you shall loaded some packages I might need to use
Second, downloaded the data set (I called exdata) and saved on my working directory and then read 2 different tables for the SSC and NEI;
SSC = Source Classification Code
NEI = National Emissions Inventory
```{r}

packages <- c("data.table", "reshape2", "ggplot2")
sapply(packages, require, character.only = TRUE, quietly = TRUE)

unzip("exdata.zip")

NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
```

Now you can create a table that is a subset (just Baltimore or just LA) and just ON_ROAD (for the motor vehicles) of the data in NEI.
Then you create one new table using **aggregate** for each, this table will contain type, year and sum of the values of emission. Also add a factor to differentiate them, the zip code for example
```{r}
sub_On_Road_Balt <- subset(NEI, fips == "24510" & type=="ON-ROAD")
head(sub_On_Road_Balt)
sub_On_Road_LA <- subset(NEI, fips == "06037" & type=="ON-ROAD")
head(sub_On_Road_LA)
balt_On_Road <- aggregate(sub_On_Road_Balt[c("Emissions")], list(type = sub_On_Road_Balt$type, year = sub_On_Road_Balt$year, zip = sub_On_Road_Balt$fips), sum)
head(balt_On_Road)
LA_On_Road <- aggregate(sub_On_Road_LA[c("Emissions")], list(type = sub_On_Road_LA$type, year = sub_On_Road_LA$year, zip = sub_On_Road_LA$fips), sum)
head(balt_On_Road)
```

Create a new table that will use *cbind* to combind values from Baltimore and LA
```{r}
combind <- rbind(balt_On_Road, LA_On_Road)
head(combind)
```

Finally plot the output.
No specs of the type of graphic we were suppose to make
I made a plot with year versus emmissions
Set to have different colors based on zipcode, one color for LA and one for Baltimore
Set geom to in the line format and theme to be black and white
Also added labels for the plot
In the title I used *\n* to make a 2 lines title 

```{r}
qplot(year, Emissions, data = combind, color = zip, geom= "line") + theme_bw() + ggtitle("Motor Vehicle Emissions \n (Baltimore[24510] VS  Los Angeles[06037])") + xlab("Year") + ylab("PM2.5 Levels")
```
